Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-01-21 paper.tex
Item: 6 - Edited paper to include a clearer reference to Figure 5

\section{Displacement Parameters}
The linear, or small-signal, part of an electrode-electrolyte interface is represented by a Constant Phase Element (CPE) or fractional capacitor. For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} Measurement of the CPE is made by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3. The numbering pattern used to identify each of the electrodes on the Octrode is shown in figure~\ref{fig:octrode}.
Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution.
Figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase} show magnitude and phase measurements of the CPE at each concentration.

>>>>

\section{Displacement Parameters}
The linear, or small-signal, part of an electrode-electrolyte interface is represented by a Constant Phase Element (CPE) or fractional capacitor. For simulation purposes this element is realised as an array of R-C branches.~\cite{ScottSingle2013,Morrison59,Elwakil10} Measurement of the CPE is made by sweeping the frequency of a sinusoidal stimulus across electrodes 2 and 7 of the Octrode while measuring the voltage between electrodes 2 and 3. The numbering pattern used to identify each of the electrodes on the Octrode is shown in figure~\ref{fig:octrode}.
Measurements made using this configuration allow for the quantification of a single interface impedance in series with the resistance presented by the bulk solution.
Figure~\ref{fig:CPE_Magnitude} shows the magnitude of the measured response of each of the six PBS concentrations accompanied by simulation results. Figure~\ref{fig:CPE_Phase} shows the phase response for the same measurements, again with the simulated response at each concentration. The simulated responses are generated using the optimised parameter values presented in Table~\ref{tab:CPEparams}. Those values were chosen as they give the closest match to the measured data.
